Designing Types for R, Empirically

### 2020-05-14 paper/main.tex
minor eval

%
%
\subsubsection{Subsumed Checks}

%
%
%
%
\subsection{Large-Scale Evaluation}
\label{subsec:eval}

To measure the effectiveness of our type annotation language, we designed an experiment pitting the types generated by a package's own testing code against the testing code of the package's clients.
We collected failed contract assertions in order to analyze them and perhaps identify weaknesses in our type annotation language.

%
%
\subsubsection{Experimental Design}

As mentioned earlier in this section, we configured \typetracer to infer types for all client-visible functions for each of the 412 packages in our corpus.
We loaded each of these inferred types into \contractr, and ran all example code from the reverse dependencies of these popular packages.
\AT{As discussed in genthat}, running R code can be tricky, as runnable code may depend on e.g. data present in a hard-coded directory structure, and we employed similar strategies to ensure that we ran as much code as possible.
\AT{Maybe Filip can write a few sentences on this, or write me a message and I can work it in.}

\contractr was equipped to provide a list of all failed contract assertions, complete with diagnostic information (including a stack trace) to help us make sense of the failed assertion.

>>>>

%
%
%
%
\subsection{Evaluation of Types from Traces}
\label{subsec:eval}

\AT{Me}

In the last section, we evaluated our type annotation language based on a set of function types that were automatically generated by \typetracer.
Now, we're interested in knowing how representative our trace-generated types are of the functions they were generated for.
To measure this, we conducted a large-scale experiment: for each package in the corpus discussed in Section~\ref{sec:corpus}, we ran \typetracer on its test, example, and vignette code, obtaining types for package functions, and then subsequently ran the test, example, and vignette code of each of the package's reverse dependencies (or clients).
We collected failed contract assertions in order to analyze them and perhaps identify weaknesses in our type annotation language.
